Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Initial light pass at rewriting carbonate threshold result section

The number of years reefs maintain coral cover above a required carbonate budget level
substantially decreases as the required carbonate budget threshold (as a percentage of reef
area) increases. Reefs with greater median depth levels maintain coral cover above required
carbonate budget levels for longer than reefs at shallow depths
[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
with the number of years a reef maintains coral cover above the required threshold
[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
decreases as the required carbonate budget threshold increases. This is likely due to an
increasing number of reefs being unable to maintain coral cover above threshold levels as
the threshold increases. There are no clear relationships between reef total connectivity
levels and the number of years reefs maintain coral cover above carbonate budget threshold
levels [@sfig-access-esm1-5-conn-carbonate]. Reef log (natural) total connectivity strength
has no correlation with the number of years a reef maintains cover above the required
thresholds. Log connectivity strength - carbonate budget maintainence correlation slightly
decreases as the required carbonate budget threshold increases.

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median timeseries using
ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
width="`{julia} carb_width`"}

>>>>

As one might expect, the number of years above $\beta_{0}$ (the assumed positive carbonate
budget threshold) substantially decreases as $\beta_{0}$ increases.

Reefs with greater median depth levels maintain coral cover above
indicative carbonate budget levels for a longer time frame compared to reefs with shallower
median depths [@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate
positive correlation with the number of years a reef maintains coral cover above the
required threshold [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget
maintainence correlation decreases as the required carbonate budget threshold increases.
This is likely due to an increasing number of reefs being unable to maintain coral cover
above threshold levels as the threshold increases. There are no clear relationships between
reef total connectivity levels and the number of years reefs maintain coral cover above
carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate]. The natural log of
total connectivity strength was found to have no correlation with the number of years a reef
maintains cover above the required thresholds. Log connectivity strength - carbonate budget
maintainence correlation slightly decreases as the required carbonate budget threshold
increases.

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025
to 1. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median timeseries using
ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
width="`{julia} carb_width`"}
